---
title: "penguins"
author: "kimberly yom"
date: "2022-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
#no quotes in tidyverse, calling for package
#to install, install.packages in the console("packagename") in quotes. Just typed in console install.packages("palmerpenguins), so now I can call for it
library(palmerpenguins)
```

typing view(penguins) in the console brings up the data frame

```{r}
#first 6 lines
head(penguins)
#last 6 lines
tail(penguins)
```

Scatterplot of body mass versus flipper length:

```{r}
ggplot(data = penguins, aes(x = body_mass_g, y = flipper_length_mm)) + geom_point(aes(color = species), size = 1)  + 
  facet_wrap(~island) +
  theme_minimal() +
  labs(
    x = "body mass in grams", y = "flipper length in mm", title = "Graph of Palmer Penguins")
#this tells us that the color is dependent on the species
#~ means "as the different functions of island", makes three separate panels for islands
```

anytime you want to change any part of a graph's aesthetics based on variables, you do it through aes (see previous code chunk). You can put it out of the aes(), but then it's not dependent on a variable. If it's referring to a variable it goes in aes() if it's not referring to a variable it goes outside of aes, ex. ggplot(data = penguins, aes(x = body_mass_g, y = flipper_length_mm)) + geom_point(aes(color = species), size = 4) + facet_wrap(\~island)+ theme_minimal() + labs(x = "Body Mass in Grams", y = "Flipper Length (mm)", title = "Penguin Graphs")

will generate a constant dot size of 4 for all penguins, adds panels for the different islands, added a minimal theme, adds labels to the axis and graph title

#### In a new code chunk, create a ggplot graph of penguin bill length versus bill depth (using the penguins dataset in the palmerpenguins package), with point color dependent on species. You should attach the tidyverse and palmerpenguins package in your .Rmd setup chunk. Update labels and add a title.

```{r}
ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm)) + geom_point(aes(color = species)) +
  labs(x = "Bill Length in mm", y = "Bill Depth in mm", title = "Scatterplot of Penguins by Bill Length and Bill Depth")
```

#### In a new code chunk, make a jitterplot of flipper length by species (species on the x-axis, flipper length on the y-axis). Update axis labels and add a title.

```{r}
ggplot(data = penguins, aes(x = species, y = flipper_length_mm)) + geom_jitter(aes(color = species))+
  labs(x = "Penguin Species", y = "Flipper Length in mm", title = "Plot of Penguin Flipper Lengths by Species")
#geom_jitter is random space between each point, same data as geom_point, but better for aesthetic purposes
```

