---
title: "penguins"
author: "kimberly yom"
date: "2022-08-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
#no quotes in tidyverse, calling for package
#to install, install.packages in the console("packagename") in quotes. Just typed in console install.packages("palmerpenguins), so now I can call for it
library(palmerpenguins)
```

typing view(penguins) in the console brings up the data frame

```{r}
#first 6 lines
head(penguins)
#last 6 lines
tail(penguins)
```

Scatterplot of body mass versus flipper length:

```{r}
ggplot(data = penguins, aes(x = body_mass_g, y = flipper_length_mm)) + geom_point(aes(color = species), size = 1)  + 
  facet_wrap(~island) +
  theme_minimal() +
  labs(
    x = "body mass in grams", y = "flipper length in mm", title = "Graph of Palmer Penguins")
#this tells us that the color is dependent on the species
#~ means "as the different functions of island", makes three separate panels for islands
```

anytime you want to change any part of a graph's aesthetics based on variables, you do it through aes (see previous code chunk). You can put it out of the aes(), but then it's not dependent on a variable. If it's referring to a variable it goes in aes() if it's not referring to a variable it goes outside of aes, ex. ggplot(data = penguins, aes(x = body_mass_g, y = flipper_length_mm)) + geom_point(aes(color = species), size = 4)  + 
facet_wrap(~island)+
theme_minimal() + 
labs(x = "Body Mass in Grams", y = "Flipper Length (mm)", title = "Penguin Graphs") 

will generate a constant dot size of 4 for all penguins, adds panels for the different islands, added a minimal theme, adds labels to the axis and graph title

```{r}
ggplot(data = penguins, aes(x = bill_length_mm, y = bill_depth_mm)) + geom_point(aes(color = species)) +
  labs(x = "Bill Length in mm", y = "Bill Depth in mm", title = "Scatterplot of Penguins by Bill Length and Bill Depth")
```

